A Dependently Typed Multi-Stage Calculus\thanks{Supported by organization x.}

### 2019-06-09 main.tex
Revice quote and unqote.

The organization of this paper is the following.
Section 2 gives an informal overview of \LMD.
Section 3 defines the syntax, type system, full reduction, evaluation contexts of \LMD.
Section 4 shows the properties of \LMD including Unique Decomposition.
Section 5 discusses future works.
Finally, Section 6 discusses related works.
\section{Informal Overview of \LMD}

In this section, we check \LMD informally after checking \LTP and \LLF which are the basis of \LMD.

\subsection{\LTP}

@@

In \LTP, quote and unquote are written $\TB_\alpha M$ and $\TBL_\alpha M$, respectively.
The type of $\TB_\alpha M$ is $\TW_\alpha \tau$ when $M$ has $\tau$ type.
The type of $\TBL_\alpha M$ is $\tau$ when $M$ has $\TW_\alpha \tau$.
Please notice that $\TBL_\alpha M$ is well-typed, $M$ has a code type from the typing rule of \LTP.
In addition to normal $\beta$-reduction, there is a reduction rule for unquoted quoted code.
\begin{align*}
    \TBL_\alpha (\TB_\alpha M) \longrightarrow M
\end{align*}
It means when a quoted code fragment is unquoted, it returns back to the original code fragment.
This reduction is called $\longrightarrow_\Lambda$ in \LMD.
\red{この文はここに来るべきなのか? LTPの説明ではないが}

>>>>

The organization of this paper is the following.
Section 2 gives an informal overview of \LMD.
Section 3 defines the syntax, type system, full reduction, evaluation contexts of \LMD.
Section 4 shows the properties of \LMD including Unique Decomposition.
Section 5 discusses future works.
Finally, Section 6 discusses related works.

\section{Informal Overview of \LMD}

We designed \LMD, a multistage calculus with dependent type.
\LMD is based on \LTP\cite{Hanada2014} by Hanada and Igarashi, which is a multistage calculus with CSP and
we introduced dependent types based on \LTP\cite{attapl}.
In this section, we check \LMD informally after checking \LTP and \LLF which are the basis of \LMD.

\red{\LTP\cite{Hanada2014}が頻発するが同一論文の複数回引用に何かルールはあるのか?}
\subsection{\LTP}

@@

\LTP\cite{Hanada2014} is a multistage calculus with CSP by Hanada and Igarashi.
In \LTP, brackets and escape are written $\TB_\alpha M$ and $\TBL_\alpha M$, respectively.
The type of $\TB_\alpha M$ is $\TW_\alpha \tau$ if $M$ has type $\tau$.
The type of $\TBL_\alpha M$ is $\tau$ if $M$ has $\TW_\alpha \tau$.
% Please notice that if $\TBL_\alpha M$ is well-typed, $M$ has a code type from the typing rule of \LTP.
In addition to normal $\beta$-reduction, there is a reduction rule for brackets and escape.
\begin{align*}
    \TBL_\alpha (\TB_\alpha M) \longrightarrow M
\end{align*}
It means escape cancels brackets.
% This reduction is called $\longrightarrow_\Lambda$ in \LMD.
% \red{この文はここに来るべきなのか? LTPの説明ではないが}
